Extending the Advanced Forensic Format to accommodate Multiple Data Sources, Logical Evidence, Arbitrary Information and Forensic Workflow

### 2009-03-14 paper/paper.tex
More work on the paper. Removed compression from encrypted streams.

%\documentclass[10pt,twocolumn]{article}
\documentclass[10pt, conference]{IEEEtran}
%\IEEEoverridecommandlockouts
%\documentclass{article}
%\documentclass[12pt]{IEEEtran}
%\documentclass{elsart5p}
\usepackage{listings}
\lstset{language=Python,
	frame=single,
	captionpos=b,
	frameround=tttt,
	basicstyle=\scriptsize,
	keywordstyle=\color{black}\bfseries,
                            % underlined bold black keywords
	identifierstyle=,           % nothing happens
	commentstyle=\color{white}, % white comments
	stringstyle=\ttfamily,      % typewriter type for strings
	showstringspaces=false}     % no special string spaces

@@

% Make sure we know its a draft for now
\usepackage{draftwatermark}
\SetWatermarkFontSize{3cm}
\usepackage{fancyvrb}
%\documentclass[12pt]{article}
\usepackage{epsfig}
\usepackage[hypertexnames=false,bookmarksopenlevel=1,bookmarksopen,bookmarksnumbered,colorlinks,plainpages=false,linktocpage,linkcolor=black,citecolor=black,filecolor=black,urlcolor=black]{hyperref}
%\usepackage{natbib}
%\pagestyle{empty}
%\psdraft
%\baselineskip=20pt %Sets line spacing to 1 unit
%\bibliographystyle{elsart-num-names}
\bibliographystyle{IEEEtran}
\usepackage{cite}
\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1:}]}{\end{trivlist}}

%\begin{frontmatter}
\begin{document}
\title{Extending the Advanced Forensic Format to accommodate Multiple
  Data Sources, Logical Evidence and Forensic Workflow}
\author{Blinded for review}
%\author{M. I. Cohen\footnote{scudette@gmail.com}, Simson Garfinkel, and Bradley Schatz}
%\author{M. I. Cohen}
%\address{M. I. Cohen is a Data specialist with the Australian Federal Police, Brisbane, Australia}
%\baselineskip=20pt %Sets line spacing to 1 unit
%\end{frontmatter}
%\thanks{M. I. Cohen is a Data specialist with the Australian Federal Police, Brisbane, Australia}
\maketitle

\begin{abstract}
Forensics analysis requires the acquisition and management of many
different types of evidence material, including individual disk
drives, RAID sets, network packets, memory images, and extracted files. Often the same evidence is
reviewed by several different tools or examiners in different
locations. We propose a backwards-compatible evolutionary redesign of the Advanced
Forensic Format an open, extensible
file format for storing of evidence and interchanging analysis results
among different tools. The Forensic Interchange Format (FIF) was
designed to be simple to implement, relying on the well supported Zip
specifications for bit level file access.
\end{abstract}

\section{Introduction}

Unlike other kinds of evidence, digital evidence can be instantly lost
or corrupted if technical measures are not immediately taken to
preserve its existence and integrity. As a result, preserving digital
evidence is an important part of most digital
investigations\cite{carrier:event-based}.

In recent years there has been a steady and growing interest in the
actual file formats and containers used to store this digital
evidence. Early practitioners created exact bit-for-bit copies (``mirror disks'') employed
proprietary software systems (e.g. \cite{safeback,ilook,encase}) for
making and authenticating ``images'' of digital evidence. PyFlag\cite{pyflag}
introduced a ``seekable gzip'' format that allowed disk images to be
stored in a form that was compressed but allowed the random-access to
evidence data necessary for forensic analysis. The Advanced Forensic
Format (AFF) expanded on this idea with a forensic file format that
allowed both data and arbitrary metadata to be stored in a single
digital archive\cite{garfinkel:aff}. Recently the open source AFF
implementation library (AFFLIB) was expanded to support both
encryption and digital signatures of digital evidence\cite{garfinkel:affcrypto}.

@@

%% Raid is only one example of the application of the map stream - the
%% most important might be the ability to use sleuthkit to generate
%% block allocation tables for all the files - thereby allowing
%% arbitrary programs to read individual files without using sleuthkit
\item Direct encoding of arbitrary mapping transformations of one or
more sources to allow multiple logical views. For example, allowing
RAID volumes to be automatically reassembled from evidence files made
of the physical RAID devices.
\item A revised compression system that allows individual chunks
  within a 16MB segment to be decompressed without decompressing the
  entire segment.
\item Support for Global Distributed Evidence Management.
\end{itemize}
\end{minipage}}
\caption{Specific design goals for the next generation forensic file
  format.}
\end{figure}
\section{The Need for an Improved Forensic Format}

@@

\begin{itemize}
\item While AFF1's design stores a single disk image in each evidence
  file, modern digital investigations typically involve many seized
  computers or pieces of media. 
\item AFF1 has no provision for storing memory images or intercepted
  network packets.
\item AFF1 has no provisions for storing extracted files that is
  analogous to the EnCase ``Logical Evidence File'' (L01) format, or
  for linking evidence to web pages.
\item AFF1's encryption system leaks information about the contents of
  an evidence file because segment names are not encrypted.
\item AFF1's default compression page size of 16MB can impose significant overhead
  when accessing NTFS Master File Tables (MFT), as these structures
  tend to be highly fragmented on systems that have seen significant
  use. 
\item Although the AFF1 specification calls for a ``table of contents'' similar
  to the ZIP\cite{zip-format} ``central directory'' that is stored at the end of AFF
  files, Garfinkel never implemented this directory in the publicly
  released AFF1 implementation, AFFLIB. As a result, every header of every segment in an
  AFF file needs to be read when a file is opened. It practice this
  can take 10--30 seconds the first time a large AFF file is
  opened. (Once the file is opened, the sectors corresponding to the
  segment headers are stored in the computer's disk cache.)
\item AFF1's bit-level specification is essentially a simple container
  file specification. Given the that there are other container file
  specifications that are much more widely supported with both
  developer and end-user tools, it seemed reasonable to migrate AFF
  from its home-grown format to one of the existing standards. 
\end{itemize}

\section{Global Distributed Evidence Management}
While Garfinkel designed AFF for use on a single machine that could
both image evidence and perform analysis, the main use of AFF in
practice has been in distributed environments in which imaging and
analysis takes place in multiple locations and is performed by
multiple individuals.

Managing evidence in a globally distributed system requires the use of
globally unique identifiers. The original AFF specification assigned
each piece of evidence a unique 128-bit identifier called a GID but did
not make it clear when this identifier should be changed and when it
should remain the same.

In practice, however, global distributed evidence management requires
more than simply tracking the movement of disk images: it requires
approaches for sharing evidence to multiple disconnected
evidence, allowing offline work, and then seamlessly recombining the
work products of the analysts in a third security domain.

@@

\subsection{Migration from AFF1 to AFF4}

We have addressed these issues in three steps. First, we have extended
the AFF schema to support multiple forensic images (which are now
called \emph{streams}) in a single evidence file. Second, we replaced
AFF's ``bit-level'' format with an improved format that is more
flexible and has better existing support. Third, we are adopting
AFFLIB to implement the new schema and file format, which will allow
existing AFF-aware programs to access files written in either the old
or the new format without modification.

@@

This section discusses the AFF4 terminology.

%% Since this is the itemised definition its probably better to
%% restrict it to the basic definitions and then move most of the
%% discussion a bit later. I want to show how concepts build on one
%% another - maybe even put a UML or class diagram

\begin{itemize}
\item \emph{An AFF Object} is the basic building block of our
file format. AFF Objects have a globally unique name (URN) as described in
\cite{RFC1737}. The name is defined within the aff2 namespace, and is
made unique by use of a unique identifier generated as per
RFC4122\cite{rfc4122}.

@@

% Is it important to define this? do we use it?
%\item \emph{An Evidence Set} is a loose collection of one or more Evidence
%Volumes.

%Evidence Sets can also be stored in object storage system (such as
%  Amazon S3), or a hybrid---for example, metadata stored in an SQL
%  database with physical data stored in large files in a file
%  system.

% I would describe this process after the definitions.

%\item \emph{An Evidence Set UUID} is a unique identifier generated
%  according to RFC4122\cite{rfc4122} for each new Evidence
%  Set. Multiple Evidence Volumes that make up the same Evidence Set
%  should all have the same UUID. When an Evidence Set is opened all its volumes are
%  loaded, their UUIDs are checked, and all of their contents are
%  logically merged so as to be visible as if they were all found in
% the same volume.

%% I Wonder if this explaination should be postposed to the section we
%% actually discuss it - otherwise we duplicate it again
%% \item \emph{An image stream} is a stream that is dedicated to storing evidence from a single
%%  source of data.  For example, a stream may contain a disk image or a network
%%  capture. Whereas AFF could only support a single stream in an evidence
%%  file, AFF4 allows any number of streams to be stored. Each stream in
%%  the archive is  given a unique identifier.

%%\item \emph{A bevy} is a specific segment that is used to hold
%%  forensic image data, such as disk sectors, memory pages, or network
%%  packets. AFF1 used the term ``pages'' to describe bevys, but this
%%  term caused confusion when AFF was used to hold memory images, hence the
%%  new term.

%% This is no longer correct - segment names are URNs and are encoded
%% according to RFC1737 as mentioned above.
%%\item \emph{A segment name} is the name under which a segment is
%%  stored within the archive. AFF4 segments have two-part names that
%%  typically contain a \emph{stream name} and \emph{bevy number}. For
%%  example the segment named \texttt{default/000001} refers to the stream
%%  called \texttt{default} and has a chunk name of \texttt{000001}. All segment
%%  names are encoded using UTF8. AFFLIB is being modified to allow any
%%  stream to be opened using the \texttt{af\_open} function; if a
%%  stream name is not specified, AFF4 implementations will open the
%%  stream named ``default.''

%%\item \emph{The segment timestamp} is a timestamp for the segment
%%  recorded in GMT.

%% This should be discussed as a way we are storing the RDF triples,
%% rather than as a definition.
%% \item \emph{Attributes} are a list of key/value pairs stored in each
%% stream's ``properties'' segment (e.g. ``stream/properties''). The
%% ``properties'' file is a text file which stores attributes one on each
%%line. Attribute lines consist of the key, immediately followed by
%%``='' for text values or ``:'' for binary values. This is immediately
%%followed by the encoded value. Values containing text are encoded
%%using UTF8, while values containing binary data are encoded using
%%Base64. There may be multiple values for each attribute; in these
%%cases the order is preserved
%%by implementations. Implements may present different keys may be
%%presented in any order, however.
%%\vspace{1ex}

%% This is not correct any more as volumes must store their own URN in
%% a different way (the zip implementation uses an archive comment for
%% this).

%% Each AFF4 archive must also have a top-level set of attributes---that
%% is, there is always a segment named ``properties.'' These volume
%% attributes are used to specify a Unique Identifier (UUID). (AFF1
%% stored each property in its own named segment. This created
%% significant overhead in many situations.)

%% Since target references are all just URNs now the resolving is automatic.

\item \emph{A Target Reference} is a way of referencing objects by use
of a Uniform Resource Identifier (URI). The URI can be another AFF
Object URN or may be a more general Uniform Resource Locator (URL),
such as for example a HTTP or FTP object.

\item \emph{The Resolver} is a central data store which collects and resolves
attributes for the different AFF Objects. We discuss the Resolver in
detail in Section \ref{resolver}.

%%in a number of places which will be highlighted below. Using
%%references it is possible for the FIF file to refer to objects
%%embedded within itself, or within other FIF files. Its is also
%%possible to refer to external flat files. A number of usage scenarios
%%are described in Section \ref{usage_scenarios}. 
\end{itemize}

Since AFF Objects have globally unique URNs it is possible for an
Object in one volume to refer to an object in another volume. The
resolver has visibility of all URNs and their current physical
location.

%The Target Reference is an important AFF4 innovation: this mechanism
%gives AFF4 files a way for describing evidence that is stored in
%different evidence volumes, in the host computer's file system, or on
%the Internet. We have defined the following target reference schema:

\label{target_reference}

%\begin{itemize}
%\item A reference in the format {\em aff://UUID/stream/segment} refers
%to an external Evidence file set (identified by its UUID). If the segment
%is missing (i.e. the reference ends with a ``/''), the reference is
%for the entire stream. We do not specify a way of actually resolving
%the UUID into a physical locations. This can achieved by
%implementations using many methods, such as Active Directory, LDAP,
%DNS, flat files or SQL databases.

%\item A reference starting with {\em file://} refers to an external
%file. The external file reference must be sanitised (to remove
%.. directory traversal) and rooted at the current directory. A
%filename of ``.'' refers to the current FIF volume.

%\item A reference starting with {\em http://} refers to a HTTP
%object which will be fetched. Support for this is optional.

%% This is no longer correct as all segments, streams and volumes have
%% a unique URN so we dont need to make these distinctions.

%% \item A references ending with a ``/'' signifies a reference to a
%% stream in the current FIF file. The stream will be opened in its
%% entirety. If the reference does not end with a ``/'', the reference is
%% for a single segment.
%%\end{itemize}

\section{Metadata and the Universal Resolver}
The AFF4 model treats metadata as an abstract concept which may exists
independently from the data itself. We term {\em metadata} to be a set
of statements about objects, written in triple notations (Subject,
Attribute, Value), where {\em Subject} is the URN of the object the
statement is made about. Using this system we are able to store
arbitrary attributes about any object in the AFF4 universe.

@@

When the volume is loaded, the AFFLIB implementation automatically
loads any properties files and populates its Universal Resolver with
the information it has visibility of. AFFLIB provides a mechanism to
use an external resolver stored on a MySQL database to provide a
Universal Resolver that shares information between different instances
on the same network.

Each URN within the AFF4 universe must have an ``\texttt{type}''
attribute to denote the type of the Object.

\begin{lstlisting}[
	caption=Example properties files for several AFF4 objects (URNs are
shortened for illustration).,
	label=image_metadata,
	float=tb,
	 ]
Directory Volume:
  urn:aff2:f901be8e-d4b2 aff2:stored=http://../case1/
  urn:aff2:f901be8e-d4b2 aff2:type=directory

ZipFile Volume:
  urn:aff2:98a6dad6-4918 aff2:stored=file:///file.zip
  urn:aff2:98a6dad6-4918 aff2:type=zip

Image Stream:
  urn:aff2:83a3d6db-85d5 aff2:stored=urn:aff2:f901be8e-d4b2
  urn:aff2:83a3d6db-85d5 aff2:chunks_in_segment=256
  urn:aff2:83a3d6db-85d5 aff2:chunk_size=32k
  urn:aff2:83a3d6db-85d5 aff2:type=image
  urn:aff2:83a3d6db-85d5 aff2:size=5242880

Map Stream:
  urn:aff2:ed8f1e7a-94aa aff2:target_period=3
  urn:aff2:ed8f1e7a-94aa aff2:image_period=6
  urn:aff2:ed8f1e7a-94aa aff2:blocksize=64k
  urn:aff2:ed8f1e7a-94aa aff2:stored=urn:aff2:83a3d6db-85d5
  urn:aff2:ed8f1e7a-94aa aff2:type=map
  urn:aff2:ed8f1e7a-94aa aff2:size=0xA00000

Link Object:
  map aff2:target=urn:aff2:ed8f1e7a-94aa
  map aff2:type=link
\end{lstlisting}

@@

The Directory Volume uses the {\em aff2:stored} attribute to provide a
base URL. The URL for each segment is then constructed by appending
the escaped segment URN to the base URL. Note that there is no
restriction on what type of URL this can be, so it may be a location
on a filesystem (e.g. {\em file://some\_directory/}) or a location on a
HTTP server (e.g. {\em http://intranet.server/some\_path}). In this
way its possible to move the entire volume from a filesystem to a web
server transparently.

@@

\subsection{ZIP64}
For AFF4, we have changed the default volume container file format to
ZIP64\cite{zipspecs}. There are many reasons for this decision:

\begin{itemize}
\item There is already wide support for the ZIP and ZIP64 formats. By
  migrating to these formats, we can take advantage of the rich number
  of user and developer tools already available. The volume may be
inspected using any number of commercial zip application (e.g. Windows
Explorer natively supports Zip files).

%% In not sure how this is relevant
%\item ZIP64 includes a CRC32 and timestamp for each segment. We
%  believe that the additional integrity checks and timestamps will be
%  useful in a forensic environment.

\item ZIP64 already includes support for the ``table of contents''
  envisioned but never implemented by Garfinkel; ZIP64 calls this
  table the ``Central Directory.'' It is written at the end of the
  ZIP64 volume.

\item ZIP64 libraries are readily available making proprietary implementations of
interfaces to the AFF4 volume format simple to write. For example, a
simple python program to dump out an Image stream is illustrated in
Listing \ref{python_code}.

@@

\begin{figure}[]
  \begin{center}
  \mbox{\epsfxsize=0.8\columnwidth \epsffile{zip_structure.eps}}
  \caption{The basic structure of a Zip archive}
  \label{zip_structure}
  \end{center}
\end{figure}

It is important to note that AFF4 only requires that the volume be
capable of storing multiple named segments of data. Although our AFF4
implementation uses the ZIP64 file format as an underlying storage
mechanism, our system also supports legacy AFF1 volumes as well as
segments that are stored in other storage systems---for example,
Amazon.com's Simple Storage System (S3)\cite{s2-aws-home-page-money}.

\subsection{Unused ZIP64 Features}
There are a number of aspects in the Zip file format specifications
which we do not utilize.
\begin{itemize}
\item We ignore Zip64's built-in support for splitting
archives into multiple ZIP files. Instead, our implementation treats
each volume as complete and stand-alone ZIP file. The AFF4
implementation then considers the segments contained within as
belonging to the universal collection. We provide the ability to split
a stream across volumes automatically, as each segment may be stored
in a different volume, and the Universal Resolver is used to find it.

\item Although Zip64 also defines encryption and authentication
extensions, we do not use them due to the restrictions imposed on
their use and because they lack of functionality that is important for
forensic user. Instead, we use AFF1's digital signature facilities for
integrity and non-repudiation, and we introduce a new stream based
encryption scheme for ensuring data privacy
(Section~\ref{crypted_stream}).

@@

%% Im not sure this is really that relevant here. Byte range updates
%% can be achieved by an append and a map operation, which might be a
%% better option for aimager working in dd_rescue mode.

%\subsubsection{A Forensically Sound Strategy For Updating ZIP64 Files}
%In many forensic applications, individual segments within the volume
%need to be updated. To this end, Garfinkel implemented several
%``update'' functions in AFF1\cite{garfinkel:aff}.

%There were two problems with the original AFF updating approach:
%\begin{itemize}
%\item Updates can cause the volume to
%become fragmented as holes appear within the middle of the volume, and
%updated segments are added at the end.
%\item Updates could be performed silently, raising questions of
%  forensic soundness.
%\end{itemize}

>>>>

%\documentclass[10pt,twocolumn]{article}
\documentclass[10pt, conference]{IEEEtran}
%\IEEEoverridecommandlockouts
%\documentclass{article}
%\documentclass[12pt]{IEEEtran}
%\documentclass{elsart5p}
\usepackage{listings}
\usepackage{times}
\lstset{language=Python,
	frame=single,
	captionpos=b,
	frameround=tttt,
	basicstyle=\scriptsize,
	keywordstyle=\color{black}\bfseries,
                            % underlined bold black keywords
	identifierstyle=,           % nothing happens
	commentstyle=\color{white}, % white comments
	stringstyle=\ttfamily,      % typewriter type for strings
	showstringspaces=false}     % no special string spaces

@@

% Make sure we know its a draft for now
\usepackage{draftwatermark}
\SetWatermarkFontSize{3cm}
\usepackage{fancyvrb}
%\documentclass[12pt]{article}
\usepackage{epsfig}
\usepackage[hypertexnames=false,bookmarksopenlevel=1,bookmarksopen,bookmarksnumbered,colorlinks,plainpages=false,linktocpage,linkcolor=black,citecolor=black,filecolor=black,urlcolor=black]{hyperref}
%\usepackage{natbib}
%\pagestyle{empty}
%\psdraft
%\baselineskip=20pt %Sets line spacing to 1 unit
%\bibliographystyle{elsart-num-names}
\usepackage{cite}
\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1:}]}{\end{trivlist}}

%\begin{frontmatter}
\newcommand{\omitt}[1]{}
\begin{document}
\title{Extending the Advanced Forensic Format to accommodate Multiple
  Data Sources, Logical Evidence, Arbitrary Information and Forensic Workflow}
\author{Blinded for review}
%\author{M. I. Cohen\footnote{scudette@gmail.com}, Simson Garfinkel, and Bradley Schatz}
%\author{M. I. Cohen}
%\address{M. I. Cohen is a Data specialist with the Australian Federal Police, Brisbane, Australia}
%\baselineskip=20pt %Sets line spacing to 1 unit
%\end{frontmatter}
%\thanks{M. I. Cohen is a Data specialist with the Australian Federal Police, Brisbane, Australia}
\maketitle

\begin{abstract}
Forensics analysis requires the acquisition and management of many
different types of evidence material, including individual disk
drives, RAID sets, network packets, memory images, and extracted
files. Often the same evidence is reviewed by several different tools
or examiners in different locations. We propose a backwards-compatible
evolutionary redesign of the Advanced Forensic Format an open,
extensible file format for storing and sharing of evidence, arbitrary
case related information and analysis results among different
tools. The new specification was designed to be simple to implement,
allowing the use of the well supported Zip File format specifications
for bit level file access.
\end{abstract}

\section{Introduction}
Unlike other kinds of evidence, digital evidence can be instantly lost
or corrupted if technical measures are not immediately taken to
preserve its existence and integrity. As a result, preserving digital
evidence is an important part of most digital
investigations\cite{carrier:event-based}.

In recent years there has been a steady and growing interest in the
actual file formats and containers used to store this digital
evidence. Early practitioners created exact bit-for-bit copies
(``mirror disks'') employed proprietary software systems
(e.g. \cite{safeback,ilook,encase}) for making and authenticating
``images'' of digital evidence. PyFlag\cite{pyflag} introduced a
``seekable gzip'' format that allowed disk images to be stored in a
form that was compressed but allowed the random-access to evidence
data necessary for forensic analysis. The \emph{sgzip} format does not
store any metadata at all.

The Advanced Forensic Format (AFF) expanded on this idea with a
forensic file format that allowed both data and arbitrary metadata to
be stored in a single digital archive\cite{garfinkel:aff}. The EWF
file format also provides for a small number of predefined metadata
fields to be stored within the file format.

Both of these approaches are limited in their expressiveness, by
nature of their (property, value) data model. The subject of the
properties is implicitly the single image contained within the
evidence container. Clearly an implicit subject metadata model is
inadequate for storing and managing multiple evidence sources
simultaneously.

The Sealed Digital Evidence Bags architecture of Schatz proposed an
approach to digital evidence containers that facilitated composition
of evidence and arbitrary evidence related information, through a
simple data model and globally unique referencing
scheme\cite{schatz:sdeb}.

The AFF4 metadata model described in this work, is based on (subject,
property, value) statements. An explicitly defined subject (identified
by an AFF4 URN) allows one to not only associate traditional EWF style
metadata with a contained image, but to also define new information
entities representing both real world and virtual entities related to
the matter. For example, an AFF4 compliant hard disk acquisition tool
should, in addition to storing an image, store entities representing
and describing the tool itself, the operator of the tool, the user
supplied parameters supplied to the tool, and the drive being imaged.

Recently the open source AFF implementation library (AFFLIB) was
expanded to support both encryption and digital signatures of digital
evidence\cite{garfinkel:affcrypto}. Clearly, the implementation of
encryption and authentication is critical for forensic file formats.

@@

\item Direct encoding of arbitrary mapping transformations of one or
more sources to allow multiple logical views. This allows 
RAID volumes to be automatically reassembled from evidence files made
of the physical RAID devices. Maps can be created using Sleuthkit and
stored in the evidence file, thereafter allowing arbitrary programs to directly
read individual files stored in a disk image.

\item A revised compression system that allows individual chunks
  within a 16MB segment to be decompressed without decompressing the
  entire segment.

\item Support for Global Distributed Evidence Management.
\end{itemize}
\end{minipage}}
\caption{Specific design goals for the next generation forensic file
  format.}
\end{figure}
\section{The Need for an Improved Forensic Format}

@@

\begin{itemize}
\item While AFF1's design stores a single disk image in each evidence
  file, modern digital investigations typically involve many seized
  computers or pieces of media.

\item The data model of AFF1 enabled storing metadata related to the 
  contained image as (property, value) pairs. This data model does
  not, however, support expressing arbitrary information about more
  than one entity.

\item AFF1 has no provision for storing memory images or intercepted
  network packets.

\item AFF1 has no provisions for storing extracted files that is
  analogous to the EnCase ``Logical Evidence File'' (L01) format, or
  for linking evidence to web pages.

\item AFF1's encryption system leaks information about the contents of
  an evidence file because segment names are not encrypted.

\item AFF1's default compression page size of 16MB can impose significant overhead
  when accessing NTFS Master File Tables (MFT), as these structures
  tend to be highly fragmented on systems that have seen significant
  use.

\item Although the AFF1 specification calls for a ``table of contents'' similar
  to the Zip\cite{zip-format} ``central directory'' that is stored at
  the end of AFF files, Garfinkel never implemented this directory in
  the publicly released AFF1 implementation, AFFLIB. As a result,
  every header of every segment in an AFF file needs to be read when a
  file is opened. It practice this can take 10--30 seconds the first
  time a large AFF file is opened. (Once the file is opened, the
  sectors corresponding to the segment headers are stored in the
  computer's disk cache.)

\item AFF1's bit-level specification is essentially a simple container
  file specification. Given the that there are other container file
  specifications that are much more widely supported with both
  developer and end-user tools, it seemed reasonable to migrate AFF
  from its home-grown format to one of the existing standards.

\section{Global Distributed Evidence Management}
While Garfinkel designed AFF for use on a single machine that could
both image evidence and perform analysis, the main use of AFF in
practice has been in distributed environments in which imaging and
analysis takes place in multiple locations and is performed by
multiple individuals. This is a state of affairs which mirrors common
practice in the field.

Global distributed evidence management requires
more than simply tracking the movement of disk images: it requires
approaches for sharing evidence to multiple disconnected
evidence, allowing offline work, and then seamlessly recombining the
work products of the analysts in a third security domain.

Managing evidence in a globally distributed system requires the use of
globally unique identifiers. AFF1 assigns
each piece of evidence a unique 128-bit identifier called a GID but did
not make it clear when this identifier should be changed and when it
should remain the same.

@@

\subsection{Migration from AFF1 to AFF4}
We have addressed these issues in a number of ways. First, we have
extended the AFF schema to support multiple forensic images (which are
now called \emph{streams}). It is therefore possible now to store
multiple related streams in the same volume, or to acquire mutiple
streams at the same time (e.g. network and disk data).

We replaced AFF's ``bit-level'' format with an improved format that is
more flexible and has better existing support, namely the Zip64 file
format is not adopted as a default storage format. This enhanced our
compatibility with other tools and simplifies implementations for
compatible systems.

We have also defined an information model which addresses uniquely
identifying evidence data, expressing arbitrary information and
integrating information and image data from multiple evidence volumes
at a time. This allows us to extend evidence collection and management
to a truely universal scale - allowing creation and management of a
large corpus.

We have also adopted AFFLIB to implement the new schema and file
format, which will allow existing AFF-aware programs to access images
written in either the old or the new format without modification. We
are extending the AFFLIB API to support the new information mode.

@@

This section discusses the AFF4 terminology. The AFF4 design is object
oriented, in that a few generic objects are presented with externaly
accessible behaviour. We discuss a number of implementations of these
high level concepts and show how these can be put together in common
usage cases.

\begin{itemize}
\item \emph{An AFF Object} is the basic building block of our
file format. AFF Objects have a globally unique name (URN) as described in
\cite{RFC1737}. The name is defined within the aff2 namespace, and is
made unique by use of a unique identifier generated as per
RFC4122\cite{RFC4122}.

@@

\item \emph{A Target Reference} is a way of referencing objects by use
of a Uniform Resource Identifier (URI). The URI can be another AFF
Object URN or may be a more general Uniform Resource Locator (URL),
such as for example a HTTP or FTP object. This innovation allows
objects in one volume to refer to objects in different volumes,
facilitating data fusion and cross referencing.

\item \emph{The Resolver} is a central data store which collects and resolves
attributes for the different AFF Objects. The Resolver has universal
visibility of objects from all volumes, and therefore guides
implementations in resolving external references. We discuss the
Resolver in detail in Section \ref{resolver}.
\end{itemize}

\section{Metadata and the Universal Resolver}
\label{resolver}
One of the fundamental tasks of forensics is in ensuring the
provenance of any particular piece of digital evidence, for example by
employing a chain of custody process. To assist in this, acquisition
methodologies emphasise the process of individuating evidence, and
storing it in a manner that it is easily identifiable.

Management of evidence requires on effective identififaction, with
practitioners currently employing acquisition time metadata such as
case identifiers and description fields in the EWF file format; file
and directory naming schemes, and labeling of evidence container hard
drives. Evidence may also be referred to by external means in an
inconsistent way. For example, in an investigator's case note a disk
image may be referred to by the name of the suspect (e.g. Joe's hard
disk), the case number or dates.

Such individuation schemes may be, however, problematic when
automatically managing evidence. For example, at acquisition time a
suitably unique individuator may not be selected. If that occured, at
analysis time evidence container files may need to be renamed to avoid
name collisions.

The AFF4 design adopts a scheme of globally unique identifiers for
identifying and referring to all evidence. We define an AFF4 specific
URN namespace\cite{RFC1737} for our naming scheme (\emph{urn:aff4}).
URNs can then be made unique by use of a unique identifier generated
as per RFC4122\cite{RFC4122}. For example, an AFF4 URN might be
\emph{urn:aff4:bcc02ea5-eeb3-40ce-90cf-7315daf2505e}

In this way we can identify uniquely any evidence without the change
for name collisions. Once a universal identification regime is
created, it is now possible to collect metadata about each object. The
AFF4 model treats metadata as an abstract concept which may exists
independently from the data itself. We term {\em metadata} to be a set
of statements about objects, written in triple notations (Subject,
Attribute, Value), where {\em Subject} is the URN of the object the
statement is made about. Using this system we are able to store
arbitrary attributes about any object in the AFF4 universe.

@@

When the volume is loaded, the AFFLIB implementation automatically
loads any properties files and populates its Universal Resolver with
the information visibile to it. AFFLIB provides a mechanism to use an
external resolver stored on a MySQL database to provide a Universal
Resolver that shares information between different instances on the
same network.

Each URN within the AFF4 universe must have an ``\texttt{aff4:type}''
attribute to denote the type of the Object.

\begin{lstlisting}[
	caption=Example properties files for several AFF4 objects (URNs are
shortened for illustration).,
	label=image_metadata,
	float=tb,
	 ]
Directory Volume:
  urn:aff4:f901be8e-d4b2 aff4:stored=http://../case1/
  urn:aff4:f901be8e-d4b2 aff4:type=directory

ZipFile Volume:
  urn:aff4:98a6dad6-4918 aff4:stored=file:///file.zip
  urn:aff4:98a6dad6-4918 aff4:type=zip

Image Stream:
  urn:aff4:83a3d6db-85d5 aff4:stored=urn:aff4:f901be8e-d4b2
  urn:aff4:83a3d6db-85d5 aff4:chunks_in_segment=256
  urn:aff4:83a3d6db-85d5 aff4:chunk_size=32k
  urn:aff4:83a3d6db-85d5 aff4:type=image
  urn:aff4:83a3d6db-85d5 aff4:size=5242880

Map Stream:
  urn:aff4:ed8f1e7a-94aa aff4:target_period=3
  urn:aff4:ed8f1e7a-94aa aff4:image_period=6
  urn:aff4:ed8f1e7a-94aa aff4:blocksize=64k
  urn:aff4:ed8f1e7a-94aa aff4:stored=urn:aff4:83a3d6db-85d5
  urn:aff4:ed8f1e7a-94aa aff4:type=map
  urn:aff4:ed8f1e7a-94aa aff4:size=0xA00000

Link Object:
  map aff4:target=urn:aff4:ed8f1e7a-94aa
  map aff4:type=link
\end{lstlisting}

@@

The Directory Volume uses the {\em aff4:stored} attribute to provide a
base URL. The URL for each segment is then constructed by appending
the escaped segment URN to the base URL. Note that there is no
restriction on what type of URL this can be, so it may be a location
on a filesystem (e.g. {\em file://some\_directory/}) or a location on a
HTTP server (e.g. {\em http://intranet.server/some\_path}). In this
way its possible to move the entire volume from a filesystem to a web
server transparently.

@@

\subsection{Zip64 Volumes}
For AFF4, we have changed the default volume container file format to
Zip64\cite{zip-format}. There are many reasons for this decision:

\begin{itemize}
\item There is already wide support for the Zip and Zip64 formats. By
  migrating to these formats, we can take advantage of the rich number
  of user and developer tools already available. The volume may be
  inspected using any number of commercial zip application
  (e.g. Windows Explorer natively supports Zip files).

\item Zip64 already includes support for the ``table of contents''
  envisioned but never implemented by Garfinkel; Zip64 calls this
  table the ``Central Directory.'' It is written at the end of the
  Zip64 volume.

\item Zip64 libraries are readily available making proprietary implementations of
interfaces to the AFF4 volume format simple to write. For example, a
simple python program to dump out an Image stream
(section~\ref{image_stream}) is illustrated in Listing
\ref{python_code}.

@@

\begin{figure}[tbp]
  \begin{center}
  \mbox{\epsfxsize=0.8\columnwidth \epsffile{zip_structure.eps}}
  \caption{The basic structure of a Zip archive. Also can be seen how
new archive members are added to an existing Zip File. The
Central Directory gets overwritten by the new member, and a new
Central Directory is written on the end.  }
  \label{zip_structure}
  \end{center}
\end{figure}

It is important to note that AFF4 only requires that the volume be
capable of storing multiple named segments of data. Although our AFF4
implementation uses the Zip64 file format as an underlying storage
mechanism, our system also supports legacy AFF1 volumes as well as
segments that are stored in other storage systems---for example,
Amazon.com's Simple Storage System (S3)\cite{s3-aws-home-page-money}.

\subsection{Unused Zip64 Features}
There are a number of aspects in the Zip file format specifications
which we do not utilize.
\begin{itemize}
\item We ignore Zip64's built-in support for splitting
archives into multiple Zip files. Instead, our implementation treats
each volume as a complete and stand-alone Zip file. The AFF4
implementation then considers the segments contained within as
belonging to the universal collection. We provide the ability to split
a stream across volumes automatically, as each segment may be stored
in a different volume, and the Universal Resolver is used to find it.

\item Although Zip64 also defines encryption and authentication
extensions, we do not use them due to the restrictions imposed on
their use and because they lack the functionality that is important
for a forensic user. Instead, we use AFF1's digital signature
facilities for integrity and non-repudiation, and we introduce a new
stream based encryption scheme for ensuring data privacy
(Section~\ref{crypted_stream}).

@@

\subsection{Implementing Zip64 in AFFLIB}
Although there are numerous Zip implementations available
today, we have created our own implementation using a combination of
available open source technology and our own novel contributions. We
are in the process of integrating this code into the AFFLIB library
and performing extensive regression testing.

There are many reasons to develop our own Zip64 implementation for
AFF4:

\begin{itemize}
\item Most Zip implementations do not implement the Zip64
  extensions. These extensions are required to support Evidence
  Volumes larger than 2GB.

\item Simple Zip implementations might rescan the
  Central Directory for each segment request. Since in practice there
  can be a large number of segments in a volume, it is advisable to
  have a Zip64 implementation that is optimized to storing thousands
  (or even hundreds of thousands) of segments in an efficient data
  structure. In fact our implementation uses the Universal Resolver to
  store the parsed central directory information, which means that in
  most cases we dont even need to scan the Central Directory at all.

\item While the Zip specification duplicates data found in the Central
  Directory entry in each File Header (such as filename, size, CRC
  etc), many implementations that we have examined only populate this
  information in one of these places. In the interest of robustness,
  we wanted to ensure that data stored in both locations would be
  populated to allow recovery of at least \emph{some} evidence that
  might exist in damaged volumes. If the central directory is lost, it
  is possible to scan through the volume, and locate all the Zip64
  file headers. Then its possible to repair and reconstruct the
  central directory.
